%-------------------------------------
% Resume in LaTeX (XeLaTeX)
% Author:  HF Yuan
% Project: https://github.com/xyz-yuanhf/yuan-resume
% Base on: https://github.com/mattyHerzig/mattys_resume
%          http://www.jianxu.net/en/
% License: MIT
%------------------------------------

\documentclass[a4paper, 10pt]{article}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{style/myresume}


% --------------------  START  --------------------
\begin{document}

% -------------------- HEADER --------------------
\begin{flushright}
  \setstretch{0.6}
  \item {\Calluna (+48) 665522039}  % Phone number
  \item {\Calluna mikolaj.garbowski@gmail.com}  % Email address
  \item {\Calluna \url{https://github.com/mGarbowski}}  % Homepage
\end{flushright}\vspace{-45pt}

\begin{flushleft}
  {\Calluna \fontsize{30pt}{30pt}\selectfont \textsc{Mikołaj Garbowski}}
  \noindent\rule{\textwidth}{0.4pt}
\end{flushleft}

% -------------------- EDUCATION --------------------
\sectionBlock{
\section{Education}
}{
\eduHeading
  {Faculty of Electronics and Information Technology}
  {\newline Warsaw University of Technology}
  {BSE in Computer Science}
  {2022 - 2026 \footnotesize{\textit{(planned)}}}
\itemListStart
  \myItem{Specialization: Artificial Intelligence}
  \myItem{Scholarship program \textit{studia id} 2023-2025}
  \myItem{Bachelor's thesis: \textit{Training Data Augmentation for Improving Face Recognition Quality in Real-World Conditions}}
\itemListEnd

}

% -------------------- EXPERIENCE --------------------
\sectionBlock{
\section{Experience}
}{
\internHeading
  {Hermes Data \& Software Solutions}{Warsaw, Poland}{03.2025 - present}
\itemListStart
  \myItem{Fullstack Developer}
  \myItem{Implementation of CRM system for business center}
  \myItem{TypeScript, React, Python, Django REST Framework, PostgreSQL}
\itemListEnd
\internHeading
  {Ringier Axel Springer Polska}{Warsaw, Poland}{2024.07 - 2024.09}
\itemListStart
  \myItem{Fullstack Developer (intern)}
  \myItem{Developed a production ready photo editor web application}
  \myItem{TypeScript, NodeJS, React, AWS}
\itemListEnd
\internHeading
  {Sages}{Warsaw, Poland}{2021.07 - 2021.09}
\itemListStart
  \myItem{Junior Support Engineer}
  \myItem{Worked on the deployment of Omega-PSIR system for academic institutions.}
\itemListEnd
}

% -------------------- SKILLS --------------------
\sectionBlock{
\section{Skills}
}{
\skillListStart
\justifying
\item \emph{Foreign languages}: English C2, French A2.
\item \emph{Python}: 
    Scientific and ML stack (
      \tech{numpy},
      \tech{scikit-learn},
      \tech{PyTorch},
      \tech{transformers},
      \tech{Weights \& Biases}
    ),
    Web frameworks (
      \tech{Django},
      \tech{Django REST Framework},
      \tech{FastAPI}
    ).
\item \emph{TypeScript/JavaScript}: 
    \tech{React}, 
    \tech{Redux}, 
    \tech{NodeJS}.
\item \emph{Java}: 
    \tech{Spring Framework}.
\item \emph{Other languages}: 
    \tech{C++}, 
    \tech{Rust}.
\item \emph{SQL and NoSQL databases}:
    \tech{PostgreSQL},
    \tech{ChromaDB}.
\item \emph{DevOps}: 
    \tech{Git}, 
    \tech{Docker}, 
    \tech{CI/CD}, 
    \tech{Terraform}, 
    \tech{Ansible}, 
    \tech{Azure}, 
    \tech{Linux}, 
    \tech{Bash}.
\item \emph{Other}: Machine learning, deep neural networks, language models, NLP, optimization algorithms, software architecture and engineering, modeling (\tech{UML}, \tech{BPMN}).
\skillListEnd
}

% -------------------- PROJECTS --------------------
\sectionBlock{
\section{Projects}
}{

\projHeading
{\textbf{Olivia CRM}}
{Implementation and development of CRM system for business center.}
{TypeScript, React, Python, Django/DRF, PostgreSQL}
{Hermes Data \& Software}

\projHeading
{\textbf{Photo Editor}}
{Front-end photo editing application based on Canvas API. Integrated with internal publishing system.}
{TypeScript, React, Redux, FabricJS.}
{RASP}

\projHeading
{\textbf{Face Recognition Model Research} \githubIcon{https://github.com/mGarbowski/thesis}}
{Research on techniques for improving convolutional neural network-based system quality using real-world data. Implementation of custom face recognition system.}
{Python, PyTorch, OpenCV, Dlib, Weights \& Biases.}
{Bachelor's thesis, WUT}

\projHeading
{\textbf{Predictive Model Microservice for Booking.com Clone} \githubIcon{https://github.com/mGarbowski/ium-projekt}}
{Data analysis, feature engineering, predictive model training and microservice implementation for hotel rating prediction.}
{Python, PyTorch, Scikit-learn, Pandas, FastAPI, Docker.}
{Group project, WUT}

\projHeading
{\textbf{RAG Application for Lecture Notes} \githubIcon{https://github.com/mGarbowski/llm-projekt}}
{Chatbot based on Bielik language model, using Retrieval-Augmented Generation approach.}
{Python, HuggingFace, sentence-transformers, ChromaDB.}
{Individual project, WUT}

\projHeading
{\textbf{Vehicle Evolution and Simulation} \githubIcon{https://github.com/mGarbowski/zpr-projekt}}
{Desktop application with physics engine and evolutionary algorithm.}
{C++, ImGui, SFML, Box2D.}
{Group project, WUT}

\projHeading
{\textbf{Plant Rendering Using L-Systems in OpenGL} \githubIcon{https://github.com/mbienkowsk/LSystemTreeGenerator}}
{Desktop application with GUI, 3D scene renderer.}
{OpenGL, Rust}
{Group project, WUT}

\projHeading
{\textbf{Web Application Deployment on Public Cloud} \githubIcon{https://github.com/mGarbowski/wus-lab-2}}
{Automated application deployment on Azure cloud.}
{Azure, Ansible, Terraform, Docker, Bash.}
{Group project, WUT}

% \projHeading
% {\textbf{Telecommunication Network Traffic Optimization} \githubIcon{https://github.com/mGarbowski/pzsp2-projekt}}
% {Integer programming model and web application.}
% {Pyomo, FastAPI, React, Docker.}
% {Group project, WUT}

% \projHeading
% {\textbf{Language Course Review Platform} \githubIcon{https://github.com/threescomplement/pap-projekt}}
% {Web application.}
% {Spring, React, PostgreSQL, Docker.}
% {Group project, WUT}

}

\vfill
\noindent\small I hereby consent to the processing of my personal data included in my application for the purposes of the recruitment process in accordance with the Act of 10 May 2018 on Personal Data Protection (Journal of Laws 2018, item 1000) and Regulation (EU) 2016/679 of the European Parliament and of the Council of 27 April 2016 on the protection of natural persons with regard to the processing of personal data (GDPR).

\end{document}