%-------------------------------------
% Resum in LaTeX (XeLaTeX)
% Author:  HF Yuan
% Project: https://github.com/xyz-yuanhf/yuan-resume
% Base on: https://github.com/mattyHerzig/mattys_resume
%          http://www.jianxu.net/en/
% License: MIT
%------------------------------------

\documentclass[a4paper, 10pt]{article}
\usepackage{myresume}  % Style package

% --------------------  START  --------------------
\begin{document}

% -------------------- HEADING --------------------
\begin{flushright}
  \setstretch{0.6}
  \item {\Calluna (+48) 665522039}  % Phone number
  \item {\Calluna mikolaj.garbowski@gmail.com}  % E-mail address
  \item {\Calluna https://github.com/mGarbowski}  % Home page
\end{flushright}\vspace{-45pt}

\begin{flushleft}
  {\Calluna \fontsize{30pt}{30pt}\selectfont \textsc{Mikołaj Garbowski}}
  \noindent\rule{\textwidth}{0.4pt}
\end{flushleft}

% -------------------- EDUCATION --------------------
\sectionBlock{
\section{Education}
}{
\eduHeading
  {Faculty of Electronics and Information Technology}{Warsaw University of Technology}
  {BSE in Computer Science}{2022 - 2026 \footnotesize{\textit{(expected)}}}
\itemListStart
  \myItem{Specialization: Artificial Intelligence}
  \myItem{In \textit{studia id} scholarship programme since 2023}
\itemListEnd

\eduHeading
  {Tadeusz Czacki High School No. 27}{Warsaw, Poland}
  {Mathematics, physics, computer science profile}{2019 - 2022}

}

% -------------------- INTERNSHIPS --------------------
\sectionBlock{
\section{Internships}
}{
\internHeading
  {Ringier Axel Springer Polska}{Warsaw, Poland}{2024.07 - 2024.09}
\itemListStart
  \myItem{Fullstack Developer (intern)}
  \myItem{Developed a production ready photo editor web application}
  \myItem{TypeScript, NodeJS, React, AWS}
\itemListEnd
\internHeading
  {Sages}{Warsaw, Poland}{2021.07 - 2021.09}
\itemListStart
  \myItem{Junior Support Engineer}
  \myItem{Worked on the deployment of Omega-PSIR system for academic institutions.}
\itemListEnd
}


% -------------------- SKILLS --------------------
\sectionBlock{
\section{Skills}
}{
\skillListStart
\justifying
\item \emph{Languages}: English C2, French A2.
\item \emph{Programming}: 
    {\Courier \fontsize{11pt}{11pt}\selectfont Python},
    {\Courier \fontsize{11pt}{11pt}\selectfont TypeScript},
    {\Courier \fontsize{11pt}{11pt}\selectfont Java}, 
    {\Courier \fontsize{11pt}{11pt}\selectfont C++}, 
    {\Courier \fontsize{11pt}{11pt}\selectfont SQL},
    {\Courier \fontsize{11pt}{11pt}\selectfont React},
    {\Courier \fontsize{11pt}{11pt}\selectfont Spring}.
\item \emph{Tools}:
    {\Courier \fontsize{11pt}{11pt}\selectfont Git},
    {\Courier \fontsize{11pt}{11pt}\selectfont GitHub Actions},
    {\Courier \fontsize{11pt}{11pt}\selectfont Docker},
    {\Courier \fontsize{11pt}{11pt}\selectfont Linux},
    {\Courier \fontsize{11pt}{11pt}\selectfont Bash}.
\item \emph{Other}: Machine Learning, Optimization, Design Patterns, Linear Programming, UML.
\skillListEnd
}

% -------------------- PROJECTS --------------------
\sectionBlock{
\section{Projects}
}{

\projHeading
{\textbf{Foto Editor app}}
{Front-end image editor app based on Canvas API. Integrated with internal publishing system. Using TypeScript, React, Redux, FabricJS.}
{Internship project, RASP}

\projHeading
{\textbf{Telecom network traffic optimization}}
{Mixed integer programming optimization model and web app. Using Pyomo, FastAPI, React, Docker}
{Group project, WUT}

\projHeading
{\textbf{Platform for reviewing language courses}}
{Web application. Using Spring, React, PostgreSQL, Docker.}
{Group project, WUT}

\projHeading
{\textbf{Car evolution and simulation}}
{Desktop application implementing evolutionary algorithm for optimizing car models for a simulation. Using C++, ImGui, SFML, Box2D.}
{Group project, WUT}

\projHeading
{\textbf{ID3 and ensemble models for multi-class classification problem}}
{Comparison of classic ID3 decision trees and ensemble models using One-vs-One and One-vs-Rest approach. Using Python.}
{Individual project, WUT}


}

\vfill
\noindent\small I hereby consent to the processing of my personal data included in my application for the purposes of the recruitment process in accordance with the Act of 10 May 2018 on Personal Data Protection (Journal of Laws 2018, item 1000) and Regulation (EU) 2016/679 of the European Parliament and of the Council of 27 April 2016 on the protection of natural persons with regard to the processing of personal data (GDPR).


\end{document}

